### 2018-05-09 Sections/economics_of_the_quantum_internet.tex
Latex update

	\begin{flushleft}Problem size scaling function (Sec.~\ref{sec:prob_sc_func})\end{flushleft} & \[s = f_\text{size}^{-1}(n\cdot \chi_\text{sc}(n_\text{global}))\] & \[\frac{n}{\alpha_\text{size}}\] & \[n^{\frac{1}{p_\text{size}}} \cdot {n_\text{global}}^\frac{p_\text{sc}-1}{p_\text{size}}\] & \[\alpha_\text{sc}n_\text{global} + \log\left(\frac{n}{\alpha_\text{sc}n_\text{global}}\right)\] \\

>>>>

	\begin{flushleft}Problem size scaling function (Sec.~\ref{sec:prob_sc_func})\end{flushleft} & \[s = f_\text{size}^{-1}(n\cdot \chi_\text{sc}(n_\text{global}))\] & \[\frac{n}{\alpha_\text{size}}\] & \[n^{\frac{1}{p_\text{size}}} \cdot {n_\text{global}}^\frac{p_\text{sc}-1}{p_\text{size}}\] & \[\alpha_\text{sc}n_\text{global} + \log(n)\]\[-\log(\alpha_\text{sc}n_\text{global})\] \\
